% LaTeX resume using res.cls
\documentclass[9pt]{res} % default is 10 pt

\usepackage{hyperref}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{latexsym}   % to get the \Box symbol
\usepackage{marginnote}
\usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=-15.5cm]{geometry}

\topmargin=-0.5in % start text higher on the page
\addtolength{\topmargin}{-.20in}
%\rightmargin=-0.25in
%\leftmargin=-0.2in

\setlength{\textheight}{11in} % increase text height to fit resume on 1 page

\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}}
\newcommand{\FIXME}[1]{\colorbox{yellow}{#1}}

%% Fonts
\usepackage{inconsolata}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}
%\renewcommand*\ttdefault{cmvtt}
%\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
%\usepackage[T1]{fontenc}

\makeatletter
\def\@tablebox#1{\begin{tabular}[t]{@{}c@{\extracolsep{\fill}}}#1\end{tabular}}
\makeatother

\begin{document}

\name{\huge\color{MidnightBlue}KIRA GHANDHI }

\address{
    178 Church Street\\  
    San Francisco, CA 94114 \\   
    \href{mailto:kira.ghandhi@gmail.com}{kira.ghandhi@gmail.com}  $\bullet$ (650)743-8198 $\bullet$ \url{https://github.com/kghandhi} \\
}

\begin{resume}                         
\marginnote{\section{EDUCATION}}[-0.5cm]  
\textbf{\color{Maroon}The University of Chicago}, Chicago, Illinois \\
\textbf{BS Computer Science, BS Mathematics}, 2016 \\
\vspace{-4pt}

\marginnote{\section{EXPERIENCE}}[-0.5cm]
\textit{\color{MidnightBlue}Braintree}, San Francisco, CA \\
\textbf{Software Engineer}
\hspace*{\fill} \textbf{August 2016 - Present}
\begin{itemize}
\item Led project to migrate legacy self-hosted Ruby on Rails service into a Java microservice running in AWS deployed multi-region using Kubernetes. Reduced latency of critical, throughput-constrained endpoints by 8x.
\item Launched Braintree's GraphQL API that replaces existing language-specific SDKs and handles traffic from large merchants such as Paymentus. 
\item Designed the API, add new features, and focused on scaling up the platform to handle the 10x increase in traffic (so far). 
\item Led design and execution of Braintree's Samsung Pay integration from initial brainstorming to release in 10 months. Orchestrated technical and product roadmaps and managed communication with Samsung as well as merchants interested in integrating the payment method.
\item Integrated new payment methods including Pay with Venmo, Apple Pay, and Google Pay into the core payments Ruby on Rails gateway.
\end{itemize}

\textit{\color{MidnightBlue}Sprout Social}, Chicago, IL \\
\textbf{Platform Engineer} (intern then part time) \hspace*{\fill} \textbf{June 2015 - June 2016}
\begin{itemize} 
\item Utilized MySQL, Cassandra, and Hadoop to cache, aggregate, and analyze social networking data exposed via a python REST API.
%\item Built upon existing interfaces to and cross-validated data collected from Google+, Google Analytics, Twitter, Facebook, Instagram, and LinkedIn.
\item Led research, design, implementation, and testing of a new, concurrent interface to Twitter historical data that allows users to track the popularity of keywords over time.
\item Built support for a new metric involving polling data from Instagram, storing it in HBase, and aggregating it with MapReduce to store it in Cassandra where it is accessible to the API.
\item Revamped a legacy Java system that worked with YARN to schedule Hadoop jobs to do a better job of reporting and notifying about jobs.
\end{itemize}

\textit{\color{MidnightBlue}Mission Street Manufacturing}, Santa Barbara, CA \\
\textbf{Software Engineering Intern} \hspace*{\fill} \textbf{June 2014 - August 2014}
\begin{itemize}
\item Developed agile front- and back-end in a cross-functional team for critical user-facing feature that shipped with all 3D printers allowing users to replace printing filament.
\item Full stack engineer across iOS (Swift), web services (Python/Flask), and embedded hardware (Python running on a Raspberry Pi).
\item Wrote unit, functional, and integration tests to cover both new and legacy code.
\end{itemize}

\vspace{-5pt}
\marginnote{\section{WRITING}}[-0.5cm] 
\textbf{REU in Mathematics}, \textit{University of Chicago}, Chicago, IL \hspace{\fill} \textbf{Summer 2013}
\begin{itemize} \itemsep -5pt
\item Wrote a paper entitled $``$Khovanov Homology as an Invariant" with guidance from graduate students in mathematics and the professors of the courses (paper online at \url{https://bit.ly/2HRBgYc}).
\end{itemize}
\textbf{Pay it Forward} Blog post on Braintree Medium blog. \url{https://bit.ly/2TuTNfk}.


\marginnote{\section{PROJECTS}}[-0.5cm]
\begin{itemize} 
\item \url{https://kaelen.me}, a professional website for local Jazz musician Kaelen Ghandhi. 
\item ElmMan, an implementation of Pacman in the functional programming language Elm (compiled to JavaScript, HTML and CSS): \url{https://bit.ly/2UP0Qkp}.
\item Hetris, an implementation of Tetris in Haskell, with the functional reactive programming library Helm: \url{https://bit.ly/2FoNbtO}.

\end{itemize}
\end{resume}
\end{document}